### 2014-10-08 fundamentals/impl.tex
added more details about materials and decay and info about arbitrary agent hierarchies

\subsection{Discrete Object Tracking}
% Resources, Materials (note isotope tracking, decay behavior)

@@

All operations performed on every resource object (splitting, combining,
decay, etc.) are tracked in detail.  This information includes the creating
agent for when resources are newly created and introduced into the simulation.
The parentage of each resource is also tracked. This makes it possible to
follow the travel history of resource objects as they are transferred between
agents.

>>>>

Although concept of the RIF hierarchy is provided, the \Cyclus kernel is
really designed to handle hierarchies of arbitrary depth.  It is just as easy
to run a simulation without regions and institutions (i.e.  only facilities)
or a simulation having archetypes that are the parents' of regions.  By
convention, institutions are mainly responsible for facility deployment, but
any archetype can have access to \Cyclus' agent deployment mechanism.  It easy
to implement agents that deploy copies of themselves, or that schedule their
own decommissioning.  Because regions, institutions, and facilities are all
just agents, they can all be implemented to excersize the full set of features
offerred to by the \Cyclus kernel.

\subsection{Resources and Materials}
% Resources, Materials (note isotope tracking, decay behavior)

@@

All operations performed on every resource object (splitting, combining,
decay, etc.) are tracked in detail.  This information includes the creating
agent for when resources are newly created and introduced into the simulation.
The parentage of each resource is also tracked. This makes it possible to
follow the travel history of discrete resource objects as they are transferred
between agents.

The \Cyclus kernel has built-in experimental support for decay calculations.
Materials "remember" the time since their last decay and agents are free to
invoke the decay function on them as desired to decay them to the current
simulation time.  Cyclus can currently operate in 2 decay modes with 2 other
modes likely to be added in future releases:

    \item "manual" (currently implemented) is the default mode just described where agents decay
        materials as needed.

    \item "never" (currently implemented) globally turns off all decay.  Materials' decay function
        does nothing.

    \item "periodic" (future) automatically decays all materials in a
        simulation with some fixed frequency.

    \item "lazy" (future) decays any material whenever its composition is
        viewed (e.g. an agent queries information about a material's
        $^{239}Pu$ content).

\TODO{describe decay algorithm and how it might be improved}.

\Cyclus has no notion of "tracked" nuclides.  In cyclus, a  material's
composition represents an arbitrarily large list (potentially thousands) of
nuclides.  Agents are free to treat nuclides present in materials any way they
please - including ignoring them.  It is the responsibility of archetype
developers to choose how to handle potentially full-fidelity compositions.
